---
title: "pml"
author: "Dawei Wang"
date: "Friday, August 22, 2014"
output: html_document
---

load data from training csv

```{r}
tdata <- read.csv("f:/data/practicalml/pml-training.csv")
dim(tdata)
```

filter the NA columns and the timestamp columns which unrelates the prediction.

```{r}
library(caret)
t1 <- tdata[,-grep("^X|timestamp|^min|^max|^var|^avg|^stddev|^amplitude|^kurtosis|^skewness|^new_window", names(tdata))]
```

split data into training, testing set.

```{r}
inTrain <- createDataPartition(y=t1$class, p=0.75, list=FALSE)
training <- t1[inTrain,]
testing <- t1[-inTrain,]
dim(training)
dim(testing)
```

use randomForest cross validation to see the accuracy of the method randomforest.

```{r}
library(randomForest)
mod1 <- rfcv(t1[,-grep("classe",names(t1))], t1$classe,cv.fold=5)
```

by the plot error.cv vs n.var, find rf is 100% accuracy when n.var is 8

```{r}
with(mod1, plot(n.var, error.cv, log="x", type="o", lwd=2))
```

so the randomForest is OK.
use the method randomForest to fit a model predicting the activity quality from the activity monitor

```{r}
modFit <- randomForest(classe ~ ., data=training, importance=TRUE, proximity = TRUE)
```

expected training data accuracy 100%, get the real accuracy 100%

```{r}
confusionMatrix(predict(modFit, training), training$classe)
```

expected testing data accuracy 100%, get the real accuracy 99.8%

```{r}
testingPred <- predict(modFit, testing)
confusionMatrix(testingPred, testing$classe)
```

apply the modFit to the testing.csv data, submit the answer to the course, get all of the 20 questions OK, and the accuracy is 100%

```{r}
testing <- read.csv("f:/data/practicalml/pml-testing.csv")
testingPred <- predict(modFit, testing)
```